---
title: "Combine two data frames"
author: "RwithAammar"
output: github_document
---
## 1- Install following packages
```
install.packages("dplyr")
install.packages("tidyr")
install.packages("writexl")
```

## 2- Load packages
```{r}
library(dplyr)
library(tidyr)
library(writexl)
```

## 3- Load or Import your data sets:
we will use builtin data sets of R for this purpose

```{r}
data("ToothGrowth")
data("iris")
```

## 4- To combine different column into another new dataframe, we have to use **bind_cols()** function of *dplyr*
```{r}
new_datframe <- as.data.frame(bind_cols(iris[0:50,2:4], ToothGrowth[0:50,2:3]))
tibble(new_datframe) #to view dataset
```

**iris[0:50,2:4]** shows the 0:50 (0-50 rows), 2:4 (2-4 columns) from iris data. You can use ***c(2,4,5)*** to specify columns and row numbers

## 5- Write the new data frame as an excel file
```{r}
write_xlsx(new_datframe, ".\\new_dataset.xlsx") #export excel file
```

This will make an excel file based on the current dataframe into your current working directory, therefore, set the working directory first by pressing **Ctrl+Shift+H**

# *Subscribe our youtube channel (Codanics)[https://www.youtube.com/watch?v=rPAyZJ_4X70&list=PL9XvIvvVL50E8HimtAnVL8N70MqImYOLS] for a complete Data Science COurse in R.*


