---
title: "7 Steps guide to make Publication Ready Bargraphs from Scratch (TWO-Way ANOVA)"
author: "RwithAammar"
date: "12/12/2021"
output:
  github_document: default
css: style.css
---
### This guide will show you how to make publication ready barplots with *TWO-WAY ANOVA* from scratch.

# **Group barplot with TWO-WAy ANova in R**
## Install these packages if you have not and load them:
```{r}
library(ggplot2)
library(ggthemes)
library(multcompView)
library(dplyr)
library(stats) 
```
## *1- Create/load a data set*

We will use the following built-in dataset for this example:
```{r}
data2 <- ToothGrowth
data2$dose = as.factor(data2$dose)

```

## *2- Calculating Two Way ANOVA*
```{r}
anova <- aov(len ~ supp*dose, data = data2) #two way anova
summary(anova) #represents ANOVA
```

## *3- Multiple Mean Comparison Analysis (only if you have significant differences in Two-way anova)*
```{r}
tukey <- TukeyHSD(anova)
tukey
```

## *4- Extract lettering from TWO-WAY ANOVA and Tukey's Test:*
```{r}
# compact letter display
group_lettering <- multcompLetters4(anova, tukey) #
group_lettering
group_lettering2 <- data.frame(group_lettering$`supp:dose`$Letters)
group_lettering2
```

## *5- Calculating and adding mean, sd and lettering columns to the data set:*
```{r}
mean_data2 <- data2 %>% 
  group_by(supp, dose) %>% 
  summarise(len_mean=mean(len), sd = sd(len)) %>% #to calculate mean and SD
  arrange(desc(len_mean)) #to arange in descending order
tibble(mean_data2)
mean_data2$group_lettering <- group_lettering2$group_lettering..supp.dose..Letters
```

## *6- Drawing Publication ready Barplots with TWO-WAY ANOVA*

- *Draw Basic Barplot*
```{r}
ggplot(mean_data2, aes(x = dose, y = len_mean,group=supp))  +
  geom_bar(position=position_dodge(0.9),stat = "identity", aes(fill = supp), 
           show.legend = TRUE)
```

- *Add erro Bars *(sd)* on the plot*
```{r}
ggplot(mean_data2, aes(x = dose, y = len_mean,group=supp))  +
  geom_bar(position=position_dodge(0.9),stat = "identity", aes(fill = supp), show.legend = TRUE) + #barplot
  geom_errorbar(aes(ymin = len_mean-sd, ymax=len_mean+sd),width = 0.1, position=position_dodge(0.9))
```

- *Add lettering to error bars*
```{r}
ggplot(mean_data2, aes(x = dose, y = len_mean,group=supp))+
  geom_bar(position=position_dodge(0.9),stat = "identity", aes(fill = supp), show.legend = TRUE) + #barplot
  geom_errorbar(aes(ymin = len_mean-sd, ymax=len_mean+sd),width = 0.1, position=position_dodge(0.9)) + 
  geom_text(aes(label = group_lettering, y = len_mean + sd), vjust=-0.4, position=position_dodge(0.9)) #add letters
```

- *Final Publication Ready group bar plot with TWO-Way ANOVA (Type-1)*

```{r}
#grouped barplot
p1 <- ggplot(mean_data2, aes(x = dose, y = len_mean,group=supp))  +
  geom_bar(position=position_dodge(0.9),stat = "identity", aes(fill = supp), show.legend = TRUE) + #barplot
  geom_errorbar(aes(ymin = len_mean-sd, ymax=len_mean+sd),width = 0.1, position=position_dodge(0.9)) + 
  geom_text(aes(label = group_lettering, y = len_mean + sd), vjust=-0.4, position=position_dodge(0.9)) + #add letters
  scale_fill_brewer(palette = "BrBG", direction = 1) + #theme setting
  labs(#this will add labels 
    x = "Dose",
    y = "Length (cm)",
    title = "Publication Ready Group Barplot",
    subtitle = "Made by #RwithAammar",
    fill = "Dose"
  ) +
  #facet_wrap(~supp)+
  ylim(0,35)+ #change your yaxis limits based on the letters
  ggthemes::theme_par(); p1
```

- *Publication ready grouped barplot with TWO-Way ANOVA with Facets (Type-2)*
```{r}
p2 <- ggplot(mean_data2, aes(x = dose, y = len_mean,group=supp))  +
  geom_bar(position=position_dodge(0.9),stat = "identity", aes(fill = supp), show.legend = TRUE) + #barplot
  geom_errorbar(aes(ymin = len_mean-sd, ymax=len_mean+sd),width = 0.1, position=position_dodge(0.9)) + 
  geom_text(aes(label = group_lettering, y = len_mean + sd), vjust=-0.4, position=position_dodge(0.9)) + #add letters
  scale_fill_brewer(palette = "BrBG", direction = 1) + #theme setting
  labs(#this will add labels 
    x = "Dose",
    y = "Length (cm)",
    title = "Publication Ready Group Barplot",
    subtitle = "Made by #RwithAammar",
    fill = "Dose"
  ) +
  facet_wrap(~supp)+
  ylim(0,35)+ #change your yaxis limits based on the letters
  ggthemes::theme_par(); p2
```

## *7- Saving upto 4K barplots in R*
- First choose a working directory by pressing *ctrl+shift+H* and select a folder
then run the following code to save in **.tiff**:
```{r}
tiff('Barplot_G1.tiff', units="in", width=10, height=6, res=300, compression = 'lzw')
p1
dev.off()
```

```{r}
tiff('Barplot_G2.tiff', units="in", width=10, height=6, res=300, compression = 'lzw')
p2
dev.off()
```




subscribe share our video at this (link)[https://www.youtube.com/channel/UCmNXJXWONLNF6bdftGY0Otw]



Best regards,

*Dr. Muhammad Aammar Tufail*

Google Certified Data Analyst

(Ask you questions!)